---
title: "homework4"
author: "Alice Ding"
date: "2023-11-28"
output: html_document
---
```{r imports, echo=FALSE, message=FALSE}
library(dplyr)
library(ggplot2)
library(psych)
library(cowplot)
library(GGally)
library(corrplot)
library(RColorBrewer)
library(MASS)
library(caret)
library(knitr)
library(kableExtra)
library(pROC)
```

## Overview

In this homework assignment, you will explore, analyze and model a data set containing approximately 8000 records representing a customer at an auto insurance company. Each record has two response variables. The first response variable, TARGET_FLAG, is a 1 or a 0. A “1” means that the person was in a car crash. A zero means that the person was not in a car crash. The second response variable is TARGET_AMT. This value is zero if the person did not crash their car. But if they did crash their car, this number will be a value greater than zero.

Your objective is to build multiple linear regression and binary logistic regression models on the training data to predict the probability that a person will crash their car and also the amount of money it will cost if the person does crash their car. You can only use the variables given to you (or variables that you derive from the variables provided). Below is a short description of the variables of interest in the data set:

- `INDEX`: Identification Variable (do not use) None
- `TARGET_FLAG`: Was Car in a crash? 1=YES 0=NO None
- `TARGET_AMT`: If car was in a crash, what was the cost None
- `AGE`: Age of Driver Very young people tend to be risky. Maybe very old people also.
- `BLUEBOOK`: Value of Vehicle Unknown effect on probability of collision, but probably effect the payout if there is a crash
- `CAR_AGE`: Vehicle Age Unknown effect on probability of collision, but probably effect the payout if there is a crash
- `CAR_TYPE`: Type of Car Unknown effect on probability of collision, but probably effect the payout if there is a crash
- `CAR_USE`: Vehicle Use Commercial vehicles are driven more, so might increase probability of collision
- `CLM_FREQ`: # Claims (Past 5 Years) The more claims you filed in the past, the more you are likely to file in the future
- `EDUCATION`: Max Education Level Unknown effect, but in theory more educated people tend to drive more safely
- `HOMEKIDS`: # Children at Home Unknown effect
- `HOME_VAL`: Home Value In theory, home owners tend to drive more responsibly
- `INCOME`: Income In theory, rich people tend to get into fewer crashes
- `JOB`: Job Category In theory, white collar jobs tend to be safer
- `KIDSDRIV`: # Driving Children When teenagers drive your car, you are more likely to get into crashes
- `MSTATUS`: Marital Status In theory, married people drive more safely
- `MVR_PTS`: Motor Vehicle Record Points If you get lots of traffic tickets, you tend to get into more crashes
- `OLDCLAIM`: Total Claims (Past 5 Years) If your total payout over the past five years was high, this suggests future payouts will be high
- `PARENT1`: Single Parent Unknown effect
- `RED_CAR`: A Red Car Urban legend says that red cars (especially red sports cars) are more risky. Is that true?
- `REVOKED`: License Revoked (Past 7 Years) If your license was revoked in the past 7 years, you probably are a more risky driver.
- `SEX`: Gender Urban legend says that women have less crashes then men. Is that true?
- `TIF`: Time in Force People who have been customers for a long time are usually more safe.
- `TRAVTIME`: Distance to Work Long drives to work usually suggest greater risk
- `URBANICITY`: Home/Work Area Unknown
- `YOJ`: Years on Job People who stay at a job for a long time are usually more safe

## Data Exploration

First, we'll view the summary and then we'll check if there are data points missing. Then, we'll clean the fields up to make sure they're ready for analysis.

```{r import}
training <- read.csv('https://raw.githubusercontent.com/addsding/data621/main/homework3/crime-training-data_modified.csv')
evaluation <- read.csv('https://raw.githubusercontent.com/addsding/data621/main/homework3/crime-evaluation-data_modified.csv')

summary <- as.data.frame(describe(training))
nulls <- 466 - summary['n']
nulls_pct <- nulls / 446
summary['nulls'] <- nulls
summary['nulls_pct'] <- nulls_pct
kable(summary, digits=2) |>
  kable_styling(c("striped", "scale_down")) |>
  scroll_box(width = "100%")
```